Create Regression Data

### 2022-04-22 data-cleaning/08-create-regression-data.Rmd
diff reg files

```{r}
justice_level <- justice_level %>% 
  select(case = casename, ddate2,
         justiceid, justicevot, justicemq, justicefem,
         nonftyp2, lcdisdirfem)

@@

```{r}
final <- case_level %>% 
  left_join(., justice_level, by = "case") %>% 
  select(case, ddate2:lcdisdirfem, everything())
```

@@

```{r}
box_write(final,
          file_name = "amicus-iv-regression-data.xlsx",
          dir_id = 158993526875)
```

>>>>

```{r}
justice_level <- justice_level %>% 
  select(case = casename, ddate2,
         justiceid, justicevot, justicemq, justicefem,
         nonftyp2, lcdisdirfem, cirsplit)

@@

```{r}
# start with justice_level bc this df has cases that the case_level does not
# these cases don't have amicus briefs, which is why they aren't in our data
final <- justice_level %>% 
  left_join(., case_level, by = "case") %>% 
  select(case, ddate2:cirsplit, everything())

# use this code if we don't want to include cases w/o amici
#final <- case_level %>% 
#  left_join(., justice_level, by = "case") %>% 
#  select(case, ddate2:cirsplit, everything())
```

@@

```{r}
amicus_only <- "amicus-iv-regression-data.csv"
full <- "amicus-iv-regression-data-all-cases.csv"
box_write(final,
          file_name = full,
          dir_id = 158993526875)
```
